%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[nofonts, letterpaper]{tufte-handout}

%\geometry{showframe} % display margins for debugging page layout

\usepackage{graphicx} % allow embedded images
  \setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
  \graphicspath{{img/}} % set of paths to search for images
  
\usepackage{fontspec}
  \setmainfont[Ligatures=TeX,Numbers={Proportional}]{Linux Libertine O}
  \setsansfont{Linux Biolinum O}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{multicol} % multiple column layout facilities
%\usepackage{hyperref}
%\usepackage{fancyvrb} % extended verbatim environments
%  \fvset{fontsize=\normalsize}% default font size for fancy-verbatim environments

% Change the header to shift the title to the left side of the page. 
% Replaced \quad with \hfill.  See \plaintitle in tufte-common.def
{\fancyhead[RE,RO]{\scshape{\newlinetospace{\plaintitle}}\hfill\thepage}}

\makeatletter
% Paragraph indentation and separation for normal text
\renewcommand{\@tufte@reset@par}{%
  \setlength{\RaggedRightParindent}{1.0pc}%
  \setlength{\JustifyingParindent}{1.0pc}%
  \setlength{\parindent}{1pc}%
  \setlength{\parskip}{0pt}%
}
\@tufte@reset@par

% Paragraph indentation and separation for marginal text
\renewcommand{\@tufte@margin@par}{%
  \setlength{\RaggedRightParindent}{0pt}%
  \setlength{\JustifyingParindent}{0.5pc}%
  \setlength{\parindent}{0.5pc}%
  \setlength{\parskip}{0pt}%
}

\makeatother

\title{Study Guide 07}
\author{Reproduction}

\date{} % without \date command, current date is supplied

\begin{document}

\maketitle	% this prints the handout title, author, and date

%\printclassoptions

\section{Vocabulary}\marginnote{\textbf{Study:} Pgs. 156, 456--475.} 
\vspace{-1\baselineskip}
\begin{multicols}{2}
spawning aggregation \\
semelparity \\
iteroparity \\
pelagic spawning \\
benthic spawning \\
egg mimicry \\
egg raiding \\
allopaternal care \\
ovoviviparity \\
viviparity \\
promiscuity \\
monogamy \\
polygyny \\
polyandry \\
cuckholdry \\
sneaker male \\
satellite male \\
sequential hermaphroditism \\
protandry \\
protogyny \\
synchronous hermaphroditism 
\end{multicols}

\section{Concepts}

\begin{enumerate}
	\item What are four mechanisms fishes may use to find a mate?

	\item What is the disadvantage of using bright coloration to attract a mate?

	\item Compare and contrast different types of parental care in fishes.

	\item Why is male parental care more advantageous than female parental care?

	\item Describe three strategies employed by nest-guarding males to increase chances of mating with a female.

	\item What is the primary difference between ovoviviparity and viviparity in fishes?

	\item What do most marine fishes have an extended larval stage?  How long can the larval stage last? Other than dispersal, what other hypotheses explain a lengthy larval period?  What is the disadvantage of a long larval stage?

	\item What conditions favor sneaker and satellite males as an alternative reproductive strategy?  

	\item What conditions favor semelparity over iteroparity?  Why is iteroparity most common in fishes?

	\item Why is pelagic spawning common in marine fishes but uncommon in freshwater fishes? Conversely, why is benthic spawning common in freshwater fishes?
\end{enumerate}


\end{document}