%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[nofonts, letterpaper]{tufte-handout}

%\geometry{showframe} % display margins for debugging page layout

\usepackage{graphicx} % allow embedded images
  \setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
  \graphicspath{{img/}} % set of paths to search for images
  
\usepackage{fontspec}
  \setmainfont[Ligatures=TeX,Numbers={Proportional}]{Linux Libertine O}
  \setsansfont{Linux Biolinum O}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{multicol} % multiple column layout facilities
%\usepackage{hyperref}
%\usepackage{fancyvrb} % extended verbatim environments
%  \fvset{fontsize=\normalsize}% default font size for fancy-verbatim environments

% Change the header to shift the title to the left side of the page. 
% Replaced \quad with \hfill.  See \plaintitle in tufte-common.def
{\fancyhead[RE,RO]{\scshape{\newlinetospace{\plaintitle}}\hfill\thepage}}

\makeatletter
% Paragraph indentation and separation for normal text
\renewcommand{\@tufte@reset@par}{%
  \setlength{\RaggedRightParindent}{1.0pc}%
  \setlength{\JustifyingParindent}{1.0pc}%
  \setlength{\parindent}{1pc}%
  \setlength{\parskip}{0pt}%
}
\@tufte@reset@par

% Paragraph indentation and separation for marginal text
\renewcommand{\@tufte@margin@par}{%
  \setlength{\RaggedRightParindent}{0pt}%
  \setlength{\JustifyingParindent}{0.5pc}%
  \setlength{\parindent}{0.5pc}%
  \setlength{\parskip}{0pt}%
}

\makeatother

\title{Study Guide 07b}
\author{Feeding}

\date{} % without \date command, current date is supplied

\begin{document}

\maketitle	% this prints the handout title, author, and date

%\printclassoptions

\section{Vocabulary}\marginnote{\textbf{Study:} pgs 71, 119--126, 436--437.} 
\vspace{-1\baselineskip}
\begin{multicols}{2}
detritivores \\
herbivores \\
carnivores \\
omnivores \\
euryphagous \\
stenophagous \\
monophagous \\
pharyngeal teeth \\
gill rakers 
\end{multicols}

\section{Concepts}

\begin{enumerate}
	\item What is the function of pharyngeal teeth?  Relate general size and shape of pharyngeal teeth to possible diet.

	\item What is the function of gill rakers?  How do they aid in feeding?  Relate general size, shape and numbers of gill rakers to possible diet.

	\item How does gut length relate to diet?

	\item If I give you a particular diet (e.g., monophagous for benthic snails), how much of the overall form and function of the fish could you explain to me?  Think about body shapes, fin shapes and position, type of swimming, mouth position, potential types of jaw teeth, gill rakers and pharyngeal teeth, and length of the gut.  In other words, tie it all together!
\end{enumerate}


\end{document}