%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[nofonts, letterpaper]{tufte-handout}

%\geometry{showframe} % display margins for debugging page layout

\usepackage{graphicx} % allow embedded images
  \setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
  \graphicspath{{img/}} % set of paths to search for images
  
\usepackage{fontspec}
  \setmainfont[Ligatures=TeX,Numbers={Proportional}]{Linux Libertine O}
  \setsansfont{Linux Biolinum O}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{multicol} % multiple column layout facilities
%\usepackage{hyperref}
%\usepackage{fancyvrb} % extended verbatim environments
%  \fvset{fontsize=\normalsize}% default font size for fancy-verbatim environments

% Change the header to shift the title to the left side of the page. 
% Replaced \quad with \hfill.  See \plaintitle in tufte-common.def
{\fancyhead[RE,RO]{\scshape{\newlinetospace{\plaintitle}}\hfill\thepage}}

\makeatletter
% Paragraph indentation and separation for normal text
\renewcommand{\@tufte@reset@par}{%
  \setlength{\RaggedRightParindent}{1.0pc}%
  \setlength{\JustifyingParindent}{1.0pc}%
  \setlength{\parindent}{1pc}%
  \setlength{\parskip}{0pt}%
}
\@tufte@reset@par

% Paragraph indentation and separation for marginal text
\renewcommand{\@tufte@margin@par}{%
  \setlength{\RaggedRightParindent}{0pt}%
  \setlength{\JustifyingParindent}{0.5pc}%
  \setlength{\parindent}{0.5pc}%
  \setlength{\parskip}{0pt}%
}

\makeatother

\title{Study Guide 01}
\author{The Science of Ichthyology; Form and Function}

\date{} % without \date command, current date is supplied

\begin{document}

\maketitle	% this prints the handout title, author, and date

%\printclassoptions

\section{Using the Study Guides}
The\marginnote{The pages listed below are recommended reading from Helfman to supplement your lecture notes.\\ 
	\smallskip 
	\noindent \textbf{Study:} Pgs. 3--9, 15--16, 111--118, 126.\\
	
	\smallskip
	\noindent \textbf{Required:} Webb, P. 1984. Form and function in fish swimming. Scientific American 251: 72--82. I will hand out the Webb paper in class but I will not discuss it in lecture. You are responsible for studying this paper on your own. Use the questions below as a guide.} study guides will help you learn the material.  Each study guide contains vocabulary to learn and a series of questions based on the lectures and the assigned reading from the textbook.  The guides may also contain information to supplement the lecture.  Read the study guides in advance of lecture to get familiar with the day's topic. Bring the study guide to class to see the vocabulary and questions in context of the lecture discussion.  This will help you recall the information during your regular study. I will not collect your answers to study guide questions.

\section{Vocabulary}
The vocabulary lists terms from each lecture that you learn and be able to apply in a broader context.  I will use the terms in lectures and on exams. If you do not know the terms, you may not understand the lecture or be able to answer an exam question. I expect you to use the proper vocabulary in your answers to questions on exams and assignments.  Use the terms as you learn the material.  I may not cover all terms in class or do so only in passing.  I expect that you will learn them by reading your textbook and using the terms in the context of the course material.

%\vspace{-1\baselineskip}
\begin{multicols}{2}
Cyclostomata\\
Myxini \\
Petromyzontida \\
Gnathostomata \\
Chondrichthys\\
Actinopterygii\\
Sarcopterygii\\
%\textbf{Form and Function} \\
rover-predator \\
lie-in-wait predator \\
surface-oriented \\
deep-bodied \\
eel-like \\
bottom-oriented \\
bottom rovers \\
bottom clingers \\
bottom hiders \\
flatfish \\
rattails \\
fusiform \\
compressiform  \\
\columnbreak\textbf{Morphology from lab} \\
placoid scale \\
ganoid scale \\
cycloid scale \\
ctenoid scale \\
superior mouth  \\
terminal mouth  \\
subterminal mouth  \\
inferior mouth  \\
abdominal fin position \\
thoracic fin position \\
jugular fin position \\
homocercal tail \\
lunate tail \\
heterocercal tail \\
isocercal tail 
\end{multicols}

\section{Concepts}

You should \emph{write} clear and concise answers to each question in this section.  The questions are not necessarily independent.  Think broadly across lectures to see ``the big picture.''  Study guide questions may be used as a basis for short answer or essay exam questions. I may also write exam and assignment questions that do not appear on the study guides. These are guides, not exhaustive test banks.

\begin{enumerate}
	\item Know the proper suffixes for order, suborder, and family.

	\item What are the five classes that comprise living “fishes”?\sidenote{Table 1.1 of your text gives a slightly different classification scheme. Recent molecular evidence supports the arrangement I presented in lecture. You will later learn other classes of fishes that have only fossil representatives.}

	\item Know approximately the number of orders, families, genera and species of fishes, world-wide.

	\item Explain the proper usage of the terms “fish” and fishes.”

	\item Associate various external features (fin shape, mouth position, etc) with specific functions (life styles) of different fishes.  If I give you a specific body form (e.g., rover-predator), you should be able to tell me various external features expected to be found on that the fish.
	
	\item Similarly, if I show you a fish that is representative of a particular body form, you should be able to tell me a great deal about the fish’s life style.  
\end{enumerate}

\noindent\textbf{Things to Know from “Form and Function” article in Scientific American by Paul Webb.}

\begin{enumerate}
	\setcounter{enumi}{2}
	\item What is the functional importance of narrow necking?  In what types of fishes would you expect to find it?  What forces are reduced by narrow necking?
	
	\item Sharks and tunas are fusiform cruisers, but their functional morphologies are very different.  What ecological and physiological differences exist between sharks and tunas to explain the morphological differences?
	
	\item Webb identifies three basic locomotor designs.  Each is specialized for a specific function to the exclusion of other functions.  What are the three basic designs?  What is the strength of each?  Explain how each specialized morphology is disadvantageous for the other swimming specialities.
	
	\item Why is a tuna with only a 10--15 percent successful capture rate (when striking at prey) just as successful at obtaining food as a pike, which has a 70--80 percent successful strike rate?  Where would you expect a generalist rover-predator to fall in terms of strike rate?  Why?  Would it be as successful as the tuna or pike?
\end{enumerate}

\end{document}