%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, twoside]{article}

\usepackage[left=1.2in,right=0.7in,top=0.8in,bottom=0.9in]{geometry} 
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\usepackage[singlelinecheck=false]{caption}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

% FONTS
\usepackage{fontspec}
\def\mainfont{Linux Libertine O}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setmainfont[Ligatures={Common}, Contextuals={NoAlternate}, BoldFont={* Bold}, ItalicFont={* Italic}, Numbers={Proportional}]{\mainfont}
\setmonofont[Scale=MatchLowercase]{Inconsolata} 
\setsansfont[Scale=MatchLowercase]{Linux Biolinum O} 
\usepackage{microtype}

\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{enumitem}

\newlength{\mylength}
\settowidth{\mylength}{\small{7.}}

\begin{document}
\begin{landscape}
{\small%
\begin{longtable}[l]{@{}L{5cm}L{3.5cm}L{3.5cm}L{3.5cm}L{3.5cm}L{1.9cm}@{}}
\caption*{\textbf{ZO 478/678: Grading rubric for ecological life history presentation.}}\\
\toprule
Content Areas & Unsatisfactory (0 points) & Borderline (5 points) & Satisfactory (7.5 points) & Outstanding (10 points) & Score \\ 
\midrule
\endfirsthead
\toprule
Content Areas & Unsatisfactory (0 points) & Borderline (5 points) & Satisfactory (7.5 points) & Outstanding (10 points) & Score\\ 
\midrule
\endhead
%% Row 1
\textbf{Clarity, logic  and organization:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item Title and author,
\item Distribution and range,
\item Taxonomy,
\item Food and feeding,
\item Reproduction,
\item Age and growth,
\item Environmental requirements, \emph{or}
Human relationships,
\item Summary / Conclusion.
\end{enumerate}&%
Covered $\leq$ 3 of the content areas in depth and the others either not at all or briefly. &%
Covered 4--6 of the content areas in depth and the others either not at all or briefly. &%
Covered 7--8 of the content areas in depth and the others either not at all or briefly. &%
Covered all content areas in depth.&%
\\[-1em]
\midrule
%% Row 2
\textbf{Quality of slides:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item $\leq$ 6 Sentences per slide and $\leq$ 6 words per sentence, not including citations, %
\item Citation included, \par%
\item No spelling or grammatical errors,\par%
\item Figures and tables were legible.\end{enumerate}&%
Met none of the content areas. &%
Met 1--2 of the content areas. &%
Met 3 of the content areas. &%
Met all 4 of the content areas.&%
\\[-1em]
\midrule
%% Row 3
\textbf{Delivery pace and style:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item Presentation lasted 15 minutes leaving 5 minutes for questions, \par%
\item Student’s voice was clear, \par%
\item Student had correct, precise pronunciation of terms,\par%
\item Student used slides as a guide: added more information than on slides.\end{enumerate}&%
Met none of the content areas. &%
Met 1--2 of the content areas. &%
Met 3 of the content areas. &%
Met all 4 of the content areas.&%
\\[-1em]
\midrule
%% Row 4
\textbf{Response to questions:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item Student was able to answer questions with depth and clarity.\end{enumerate}&%
Did not answer any of the questions. &%
Answered all questions but without any depth and clarity \emph{or} answered less than half with depth and clarity. &%
Answered most questions with depth and clarity. &%
Answered all questions with depth and clarity.&%
\\
\midrule
& & & & \vspace{0.5in}\par\hfill\normalsize{Total Score\phantom{m}} & \\
\bottomrule
\end{longtable}
}%End small font size

\end{landscape}
\end{document}