\midrule
%% Row 11
\textbf{Figures} Have a horizontal (bottom) and vertical (left) axis; Figure legend listed below the figure and should be self explanatory of the information contained in the figure; If you photocopy or scan one, make sure to make up your own figure legend as well, especial to make sure it fit your numbering system. symbols and units present in axes labels; see following pages for examples. If you scan or photocopy a figure, which is okay to do, be sure to cite the source of the figure and to include the citation in the Literature Cited.\par
\textbf{Tables:} Table legend located above the table itself and should be self-explanatory of the information contained in the table. If you photocopy or scan one, make sure to make up your own table legend as well, especial to make sure it fit your numbering system. Table format, if you make your own has 5 main points: 1) the number and title; 2) the vertical heading(s) (column) called boxhead; 3) the horizontal headings (row headings) called the stub; 4) the fields that have the data; 5) 3 horizontal lines across the table with 1 placed below table legend (title), 1 below the boxhead; and 1at the bottom of the table; See example Also, if you use scan or photocopy a table, which is okay to do, make sure to cite the publication you got the figure from and to include the citation in the Literature Cited. &%
No figure or table legend(s); For original tables, no horizontal lines breaking the table header from the data and or multiple vertical lines present. \textbf{NOTE TO MST: CREATE SEPARATE HANDOUT FOR TABLE FIGURE FORMATING. HAVE THIS CATEGORY REFER TO THAT HANDOUT. THAT WILL MAKE THIS MORE CONCISE.} &%
Figure and  table legend(s) only consists of the word ?Figure? or ?Table? plus whatever number it is. (e.g. Figure 1) without a description. Legend(s) may be on the top or the bottom of figure; AND/OR (If original, e.g. not scanned or photocopies) horizontal and vertical line formatting not correct. &%
Figure legends are presented at the bottom of the figure. Table legends are presented at the top of the table. Figure legend(s) include(s) the number (e.g. Fig. 1), but does not accurately describe the figure; or does not include the fig. number; or is placed above the figure itself, or does not include the citation of where you got the figure from, OR (If original, e.g. not scanned or photocopies) horizontal and vertical line formatting not correct. Table legend includes the number (e.g. Table 1), but does not accurately describe the table; or does not include the table number; or is placed below the table itself or does not include the citation of where you got the figure from, OR (If original, e.g. not scanned or photocopies) table horizontal and vertical line formatting not correct. &%
Figure legend(s) are listed below the figure. Figure legend(s) accurately describe(s) the figure(s) and provide enough information to stand-alone without referring back to the text; are located below the figure itself, and includes the citation for the source of the figure. And if original, e.g. not scanned or photocopies, have the correct horizontal and vertical line formatting. able legends (titles) has table number and accurately describes the table and provide enough information to stand alone without referring back to the text; are located above the figure itself and includes the citation of where the figure was copied from: Tables, if original, have only 3 horizontal lines, 1 below the title, one below the boxhead, and one below the last data row. \\
