%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}

\usepackage{geometry}
\geometry{letterpaper}                   
\geometry{margin=0.5in}
\usepackage[parfill]{parskip}    % Activate to begin paragraphs 
\pagenumbering{gobble}

\usepackage{fontspec}
\setmainfont[Ligatures={Common,TeX}, BoldFont={* Bold}, ItalicFont={* Italic}, BoldItalicFont={* BoldItalic}, Numbers={Proportional}]{Linux Libertine O}
\setsansfont[Scale=MatchLowercase,Ligatures=TeX]{Linux Biolinum O}
%\setmonofont[Scale=MatchLowercase]{Inconsolata}
\usepackage{microtype}

\usepackage{multicol}


\usepackage{enumitem}
\setlist{leftmargin=*}
\setlist[1]{labelindent=\parindent}


\begin{document}
\thispagestyle{empty}

\setlength\columnsep{1.5cm}
\fontsize{18}{24}\selectfont 
\begin{multicols}{2}
\begin{enumerate}[itemsep=1cm]
% Page 1
\item Long bill.\newline Little Blue Heron
\item Short bill.\newline Carolina Chickadee
\item Hooked bill.\newline Mississippi Kite
\item Crossed bill.\newline Red Crossbill
\item Compressed bill.\newline Atlantic Puffin
%\end{enumerate}

%\begin{enumerate}[resume, itemsep=1cm]
% Page 2
\item Depressed bill.\newline Northern Pintail
\item Stout bill.\newline Greater Prairie Chicken
\item Terete bill.\newline Ruby-throated Hummingbird
\item Straight bill.\newline Yellow-crowned Night-Heron
\item Recurved bill.\newline American Avocet
\item Decurved~bill. Carolina~Wren~\& \newline Long-billed Curlew
\item Bent bill. \newline Lesser Flamingo
%\end{enumerate}

%\begin{enumerate}[resume, itemsep=1cm]
% Page 3
\item Swollen bill. \newline Summer Tanager
\item Acute bill.\newline  Blackburnian Warbler
\item Chisel-like bill. \newline Yellow-bellied Sapsucker
\item Toothed bill. \newline American Kestrel
\item Serrate bill. \newline Hooded Merganser
\item Gibbous bill. \newline Surf Scoter
\item Spatulate bill.\newline  Northern Shoveler
%\end{enumerate}

%\begin{enumerate}[resume, itemsep=1cm]
% Page 4
\item Notched~bill. Wood~Thrush~\& American Robin
\item Conical bill. \newline American Goldfinch
\item Lamellate bill. \newline Lesser Scaup
\item Angulated commissure. \newline Rose-breasted Grosbeak
\item Gular sac. \newline American White Pelican
%\end{enumerate}

%\begin{enumerate}[resume, itemsep=1cm]
% Page 5
\item Square tail. \newline Sharp-shinned Hawk
\item Rounded tail. \newline American Crow
\item Graduated tail. \newline Yellow-billed Cuckoo
\item Pointed tail. \newline Ring-necked Pheasant
\item Emarginate tail. \newline Purple Finch
\item Forked tail. \newline Barn Swallow
%\end{enumerate}

%\begin{enumerate}[resume, itemsep=1cm]
% Page 6
\item Incumbent hallux. \newline Yellow-headed Blackbird
\item Elevated hallux. \newline Wild Turkey
\item Anisodactyl toes. \newline European Starling
\item Syndactyl toes. \newline Belted Kingfisher
\item Zygodactyl toes. \newline Red-bellied Woodpecker
\item Heterodactyl toes. \newline Elegant Trogon
%\end{enumerate}

%\begin{enumerate}[resume, itemsep=1cm]
% Page 7
\item Pamprodactyl toes. \newline Chimney Swift
\item Raptorial toes. \newline Red-tailed Hawk
\item Semipalmated~webbing. Photo~\& Greater Yellowlegs%\newline Semipalmated Plover (photo) and mystery plover
\item Totipalmate webbing. \newline Double-crested Cormorant
\item Palmate webbing. \newline Mallard (hybrid)
\item Lobate toes. \newline American Coot
\end{enumerate}

\end{multicols}

\end{document}  