%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt]{article}  
\usepackage[left=0.75in,right=0.75in,top=1in,bottom=0.5in]{geometry} 
\geometry{letterpaper}                   		% 
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\setlength{\parindent}{0pt}


\newif\ifprintkey
%\printkeytrue  % Instructor version with specimen location
\printkeyfalse % For student version
\newcommand{\PrintKey}[1]{\ifprintkey{\textbf{#1}}\fi}


\usepackage{graphicx}
\graphicspath{%
	{/Users/goby/Pictures/teach/466/lab/}}
	
% FONTS
\usepackage{fontspec}
\def\mainfont{Linux Libertine O}
%\defaultfontfeatures{Mapping=tex} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setmainfont[Ligatures={Common, TeX}, BoldFont={* Bold}, ItalicFont={* Italic}, Numbers={Proportional}]{\mainfont}
%\setmonofont[Scale=MatchLowercase]{Inconsolata} 
%\setsansfont[Scale=MatchLowercase]{Linux Biolinum O} 
\usepackage{microtype}



\usepackage[singlelinecheck=false]{caption}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}


%\pagenumbering{gobble}
\usepackage{enumitem}
\usepackage{multicol}
%\setlist{noitemsep}
%\setlist[description]{style=multiline, leftmargin=1.25cm, parsep=1ex}


\begin{document}
%\thispagestyle{plain}

\begin{multicols}{2}


Table 1
\begin{enumerate}
% Page 1
\item  Long bill. Little Blue Heron
\item  Short bill. Carolina Chickadee
\item  Hooked bill. Mississippi Kite
\item  Crossed bill. Red Crossbill
\item  Compressed bill. Atlantic Puffin
\end{enumerate}

% Page 2
Table 2
\begin{enumerate}[resume]
\item  Depressed bill. Northern Pintail
\item  Stout bill. Greater Prairie Chicken
\item  Terete bill. Ruby-throated Hummingbird
\item  Straight bill. Yellow-crowned Night-Heron
\item  Recurved bill. American Avocet
\item  Decurved bill. Carolina Wren and Long-billed Curlew
\item  Bent bill. American Flamingo
\end{enumerate}

% Page 3 
Table 3
\begin{enumerate}[resume]
\item  Swollen bill. Summer Tanager
\item  Acute bill. Blackburnian Warbler
\item  Chisel-like bill. Yellow-bellied Sapsucker
\item  Toothed bill. American Kestrel
\item  Serrate bill. Hooded Merganser
\item  Gibbous bill. Surf Scoter
\item  Spatulate bill. Northern Shoveler
\end{enumerate}

% Page 4
Table 4
\begin{enumerate}[resume]
\item Notched bill. Wood Thrush and American Robin
\item Conical bill. American Goldfinch
\item Lamellate bill. Lesser Scaup
\item Angulated commissure. Rose-breasted Grosbeak
\item Gular sac. American White Pelican
\end{enumerate}

% Page 5
Table 5
\begin{enumerate}[resume]
\item \item  Square tail. Sharp-shinned Hawk
\item  Rounded tail. American Crow
\item  Graduated tail. Yellow-billed Cuckoo
\item  Pointed tail. Ring-necked Pheasant
\item  Emarginate tail. Purple Finch
\item  Forked tail. Barn Swallow
\end{enumerate}

% Page 6
Table 6
\begin{enumerate}[resume]
\item \item  Incumbent hallux. Yellow-headed Blackbird
\item  Elevated hallux. Wild Turkey
\item  Anisodactyl toes. Northern Mockingbird
\item  Syndactyl toes. Belted Kingfisher
\item  Zygodactyl toes. Red-bellied Woodpecker
\item  Heterodactyl toes. Elegant Trogon
\end{enumerate}

% Page 7
Table 7
\begin{enumerate}[resume]
\item Pamprodactyl toes. Chimney Swift
\item  Raptorial toes. Red-tailed Hawk
\item  Semipalmated webbing. Semi-palmated Plover (photo) and mystery plover
\item  Totipalmate webbing. Double-crested Cormorant
\item  Palmate webbing. Mallard (hybrid)
\item  Lobate toes. American Coot
\end{enumerate}

\end{multicols}
\end{document}  